\section{Episode 4: Whores or Boars?}

Returning to Vathos Boundary, Otoria and her assorted friends are seeking passage North, and have been given a list of gangs that may have stolen all the horses.

They wake up in Marcey’s and try to decide how to proceed.

Otoria wants to infiltrate the Heights Rights lot. Gabrins wants to hassle the Fancy Men.

Riphard sits in the pub, the Gabrins run off.

Riphard wants to walk 6 months instead of finding any horses. He sits in the pub by himself to try and achieve this.

Gabrins and Otoria else goes to see the Blacksmith who’s real sad. Apparently his necklace has got stolen. Otoria wants to find it. They go off to the Blacksmith’s house and look for clues.

Pilch and Riphard bond.

CSI:Vathos ensues at Black Smith’s house. Apparently the necklace was stolen by one non-small person. The fidelity of the blacksmith remains in question.

Kolo looks for criminals to ask questions.

Riphard is pissed. It’s, like, 12:30. Pilch leaves him to his own demons and goes to wander the streets aimlessly.Then, all of a sudden he discovers something important.

Meanwhile, or earlier or something, Otoria talks to the police man and he suggests she checks the local jewelers, so see if whoever stole it tried to sell it. She says she’ll have a look.

Gabrins go into the Mos Eisley Cantena, and talk to a big orc man. Kolo tries to be tough, but is absolutely not that and gets thrown around and nearly thrown out. Then Esme gets involved and is intimidating as fuck. She tries to get the orc man to play cards to win information about the Fancy Man, but that doesn’t work. There’s all sorts of back and forth.

Then, a “Fancy” Woman appears (not a “Fancy Woman”). She offers to help the Gabrins if they come to their hideout. They say they’re going to gather everyone up and head out with her.

Pilchard found an old man. He talks to him about how things aren’t as good as they used to be. There’s also not as young a man. Their names are Casper and Germaine. They are woodsmen. He scares them by being a crazy person. There is no inquisition. He asks them if they know any benders. Pilch is a weirdo.

Otoria finds the jeweler, and the necklace, and the truth.

Riphard is pissed. Then he’s outside in the alley, propped up against the bins, with Otoria trying to kill him, and then Gabrins trying to steal his money. The Gabrins want to keep him alive, but Riphard himself doesn’t seem to have as much interest in that and tries to shoot Kolo. He misses, and Pilch turns up. Riphard tries to run and is instantly struck down. It’s tragic.

Otoria starts dragging him to the police station. Half way there she’s convinced to take him the blacksmith’s instead.

The blacksmith convinces Otoria not to take Riphard to the police, when the group tell him everything, because he would be killed by the church, attracting a lot of attention. Otoria wanted to cut him into little bits, so she’s not super happy about him getting away scot free.

The group give the blacksmith a shit ton of money, then go back to the pub. Riphard sleeps his pain away.

Gabrins stack up inside a coat, and everyone goes into the alley to meet the lady.

The lady is totally fooled by the Gabrins in the coat, for real. She insists on the group helping her or some shit before she tells them where the fancy men are.

The group head North, out of town, to Whorecity. Then west, then through some hills, then some hillocks. Then there’s a camp. It’s a little bit secret. Otoria and the lady (who’s called Delilah) get on like a horse on fire (like what happened in the stables that time).

WELCOME TO WHORECITY!

The group get taken to the Queen Whore, Mae. They brag about their wealth, insult Mae’s fashion sense and then finally get round to actually talking about why they’re there.

Djago and Mae don’t seem like besties, but Delilah jokes that they are. What’s up with that?

Exme wants to know what whoring is.

Otoria wants to know where the horses are. Mae implies, but does not say, that she knows where they are, but says they need to do work for her first.

Kolo makes a deal. No one’s quite sure what it is.

Apparently the whores buys their boots in bulk. They’re damn fine boots. We should get some.

Mae admits the Fancy Men have all the horses, and says she’ll tell them where to find the Heights Rights lot, so they can kill them, and then she’ll tell them we’re the Fancy Men are, so that they can kill them.

Otoria tells Mae not to tell anyone they’re there. Esme tells Mae that they’re terrorists planning to take down the state.

Everything seems fine.

Mae has work to plan.

The gang manage to get two horses, and squeeze on to the back of them.

Riphard gets hit on

They ride horses to Razzle’s house. Razzle is king of the Height Rights. This is his house.

Gabrins are going to go in first, like they’re HeightRightsers. They’re going to see if they can find Razzle, and then come back and do some Strats and Tats.

Gabrins enter HeightRightsManor.

There’s a fucking hobbit.

He’s going to fucking whistle like a bellend.

The Gabrins shout at him and introduce themselves, to get ahead of the scandal.

The fucking hobbit’s called Nickles.

“Big rights for small people”, says Esme.

The Gabrins tell Nickles that they’ve been persecuted for being little. Kolo has terrible flashbacks to the Cantena. This pleases Nickles and they get taken inside.

I can’t really see what’s going on any more.

There’s a sleeping area and some stairs.

Here’s Razzle. He’s a gnome. He’s got a big bag of fireworks. He’s stressful to listen to.

He’s a little leprechaun gangsta, see.

He wants to burn Djago down, see.

Esme tells everyone about wanting to bring down the church again. Razzle wants to kill humans indiscriminately. It’s a debate for the ages. Only Razzle can use the boomstick.

Esme’s, like “please”. Razzle’s like, “NO”.

Esme offers information about booms, in return for… a thing… or… anything. Hundreds of short people will die, but I think that’s the plan. I really don’t understand. It definitely sounds like they’re not going to kill this guy.

Razzle wants Gabrins to kill whores.

Razzle wants to be quiet and small. He’s failing at half of that.

Kolo wants to pick up part time job killing humans, Esme thinks they should focus on taking down church, so that they can kill even more humans.

Gabrins suggest Razzle should come with them on mission to kill whores. Razzle says no. He sends his best men, though.

The Gabrins and the best men go out into the woods, where the Bargins plan to kill them. Otoria and Pilch talk about when to kill everyone.

They eventually decide to wait until everyone’s asleep.

In the woods, everyone’s asleep. Time to die.

Pilch tries to back out of this whole thing, trying to get the Whores and Height Right’s to be friends.

Otoria wants to cut off their tongues and hands.

Esme is spread the gospel of The One, trying to convert the Best Men. Esme and the Best Man (who’s a woman) take a minute and pray to The One.

Everyone else is hanging out in the bushes.

Everyone suddenly doesn’t want to kill them any more. They feel really bad for the small people, but then they kill them anyway.

There’s a brutal massacre.

Everyone decides that they’re going to kill Razzle, but that they want the small people to be free and happy under a new ruler.

Everyone gets back to the cave and prepare for shit to go down.

TO BE CONTINUED...



\clearpage