\section{Episode 5: Pitter Patter of Tiny Bears}

[The following pages are torn from a larger volume, and hastily rebound with string - One corner is singed implying someone attempted to burn this or the entire volume.
The writing is in a quick, hurried, but practiced hand, and the type-face changes occasionally as though the writer grew bored of their style]
Codenames as follows...
- SH - Shadow Hound - Yours truly
- RP - Righteously Pissed - the drunken dwarf
- JR - Jilted Royal - the foreign lady
- SR - Shifty Rogue - the thieving goblin
- JM - Joyful Mechanic - the inventive goblin
So we’re in a cave, and just slaughtered a small number of small folk to whom we hope to ally. Great.
SR has initiated a plan to take over the small-peeps by killing Razzle, SH says we should try and discredit the small folks leader (Razzle) - Seems that the goblins and Dwarf are going to go in and try to convince everyone else that he’s gone rogue and isn’t part of the organisation anymore.
I’m loath to split the party, but the tiny bigots (...small-ots?) probably won’t like me or JR walking in - maybe we can be guards or sympathisers?
Anyway, I do the honorable thing of burning the bodies (and taking 5 ears), and then forging a document for RP -
"Razzle is accused of collusion against the SRA with his Ofecal Cherch Buziness."
We stop outside, and finalise the plan - is as above, but the goblins will go in shortly afterwards to make it seem they were (recently) ambushed.
RP Successfully enters the camp, thanks to the forged letter. The goblins sneak in after. RP manages to get found as an imposter, despite the letter. He did not know the secret Nichols handshake.
A fight breaks out between RP and 3 members of the SRA - but he’s quickly subdued.
Everyone decides to scapegoat RP as a church-worker, still to discredit Razzle. Goblins sneak in.
SRA becomes SRM - suddenly, because RP.
Goblins come in, pretending to be injured - leant huge credence by my amazing disguising. Two of the SRA fall for it.
RP gets blown up. Probably. Razzle likes bombs. “No dwarfy… I expect you to die!”
RP starts whipping people. He gets knocked out.
Team gobbo and 2 of the SRA run in. One gets blown up, the rest like Razzle more for this.
JR is very noisy, it messes up our stealthiness.
SH becomes a rock.
I get RP back up by punching him, and then dance like my life depends on it (which it did).
RP is then useful by disarming Razzle.
Razzle Shanks me, but the shadows protect.
The JM Blows off Razzles head.
SH, RP and JR (who had been doing pull-ups the whole time) leave.
The goblins appoint “Buttons” as the new leader of (this faction) of the SRA.
There's maybe 4 SRA left.
They also loot: Signet ring (with stampy well) 10 rockets 10gp
Papers - Bits of communication, Old Plans, Promotional Material, rambling letters,
I’m not happy about this.
We rest up.
Kolo and Otario have a heart to heart.
We all go to see Mae. JR takes point in the conversation. It’s interesting. Mae and Delilah plan with us to go kill fancy-pants.
I’m on a horse.
Mae gives us 3 people to go take on Fancy-Pants, Diago. One is an Battle-axe barbarian type, others a Crossbow-marksman, as is Delilah.
JR and JM also get fancy “dutty ho” boots.
On the way (to Diago) we encounter a man that tells us about the giant boar. Delilah flirts with RP for some reason.
JR - with her Mechanism Bow, JM and SR decide to attack at ranged, and take out the boar slowly.
In the forest, we get attacked by dropbears.
RP gets ripped hard. JR flails.
Me and the goblins kill nearly everything.
The crossbow whore (Martha) dies.
I save RP.
I get Martha’s Xbow.
Wait, shit… I better burn these pages - safer than leaving a paper trail... 
\clearpage