\section{Episode 6: Arbitration}

Day starts well as we are unmolested    

Pilch talks to Delilah about other men and how to lure them in, he is very keen even if it means traversing vast tracks of forest. Even the Dutty Hoe isn’t willing to put out that far.    

Camp is made, no one wants to sleep, perhaps everyone is super excited about meeting the giant pig. Kolo gets bored and falls asleep.    

Fishy loses his bird, Kolo helpfully brings it back, but it somehow escapes. I am intensely interested in how the bird works, could be proper useful to have a scout, and something to distract enemies in a fight……    

Fishy will pay for this, but first I follow Pig Smells.    

Otario and I go for sneaky first kill on Pig, which is followed by a sudden tactical climb into a tree. Otario winds up and pitches the Gabrin Fast Ball Special. Negotiations unfortunately fail, and after bouncing off the pig… watches as the Strange One leaps and pirouettes onto the big piggy before spanking it with her giant sword.    

Exmeh then lines up a shot and whispers &quot;This little piggy went to market&quot; before dispatching one baby pig.    

Before suddenly there are two Exmehs, wandering about. The Evil twin Exmeh then kills poor little piggy No 2.    

Riphard blows Big Pigs brains out everywhere, no more piggies.    

“It is Impossible to have a Cake and Also eat a Cake” Strange on is Strange.    

Barbeque pork all around, as Pilch adds to his ear collection. Big Pig is Too Big except for fatty hoe who eats most of pig. Impressive…. Riphard is strangely not interested in pig.    

After camping overnight in the pigs den, we move on to through the woods following filthy hoe Delilah. Somehow she knows where fancy man lives….    

Pilch watches Kolo taking a massive smelly pig sized shit. About half way through, kolo turns and make eye contact while pinching off the end of the loaf.    

Pilch is confused about horses and dirt hoes.    

Its agreed that all ravens will now be shot.    

Pilch is a huuuge fiilltthhhyyy liar, about where the enemy are and what they are up to.    

Otario leads the lady charge, to entrap the fancy men. While we sneaky for horses, except Riphard who walks into the camp bringing the good news of the lord.    

Things go well with the fancy pants, as Otario works her magic    

Kolo horse whispers with his own shit, and as he is tying up the horses, stoooopid Exmeh sets off a fire work. Otario then starts a song and does the dance of her people, it is not impressive.    

Exmeh stands statue of liberty esque holding a boom stick high.    

Kolo sets off a horsey train through the camp. “ A sudden Rampage “    

One bandit does his best to salve the horses, “I’ve got this lads” by running in front of them all, who then savagely kill him.    

Otario gets Axed a lot of questions, while pilch hides behind a tent and tries to convince the fancy men their leader is a nerd. Riphard starts a loaded sermon. Exmeh sends some redundant technology burning some poor fuckers face off, before hiding behind a tent!    

Pilch finally finds his ball sack, no correction he hides behind another tent before trying to reason with the enemy again. Luckily he is saved by the tent catching arrows. Strange booyagh is afoot as voices from the forest, as the horses speed out of the village.    

Raven hunt is going very badly, something is definitely up with this freaking bird. Its naked.    

Pilch somehow convinces half the archers to go to bed, while he gets nailed by Capn’ Fancy Pants, and leaking smoke.    

Otario is taking a nap on the table, while Pilch makes an ill timed verbal foray against Capn’ Fancy Pants, and as he pulls out his knife his chest explodes across across pilch from Exmehs rail gun.    

Riphard finally deals with the pesky Axe man, blowing the back of his head out.    

Sterling doesn’t make the cut because Kolo makes the world a better place with one less asshole. Pilch cuts more ears from Diegos Boys, chopping Diegos head off for good measure.    

Otario rides off into the sunset badly, Delilah suddenly decides to stick with the party. Possibly because of sexy smelly gabrins.    

Pilch gets some hot whispers from mega Hoe.    

Return to sender, to find some poor mug still getting a shoein.    

In the middle of town we discover a plate armoured individual standing over a leather clad man. She is holding a gun to the mans head. The gun is bigger and badder than Riphards, giving Riphard a massive Hard on.    

Kolo shits himself, Otario tries to take the hit, but then Riphard out of nowhere gets the game on with the Arbiter! Truth will come and Justice is serverd liberally with a massive sword.    

Otario and Riphard are totally outclassed. Otario gives a long winded speach to the crowd, while Pilch is gone, and the Gabrins are at the titty bar. It doesn’t quite go the way she planned. Not even able to take out a wooden pillar afterwards. She then stalks the scary arbiter woman.    

Riphard gets some top tips from the Scary lady. Otario gets a letter for 500 gold from Arbiter Kyross, which she lets drop to the floor to be cashed at Rivers Falls.    

Riphard gets a note, recommending him to the master at Rivers Falls. To train him up with ninjas. The idea of training with the Ninjas makes him cry. Its genuinely touching. He also pockets the 500 gold note.    

Otario continues to stalk Lady Kyross, throughout the day and night. 
\clearpage