\section{Episode 6: Mysterious Incident of the Cow in the night}

Pilch is the anonymous Jackalope, also in attendance is Anonymous Hippo and Anonymous Frog    

Hester is the owner of the caravan    

Otario is found in the town still staring at the kebab ladies house. He agrees to meet everyone at the main square for departure. In the mean time Otario pays a small urchin to send a letter everyday to convince the Kebab lady that she is still watching her    

At the caravan Kolo is upset that everyone has a caravan except for him. Exmeh locks him out. Pilch cosies up to Hestor    

Boamos under represented caravan member that Otario befriends. He is from South West Africa, which no one has ever heard of. He is happy to help learn Otario. “Otario learns horsecraft” its super effective.    

Riphard and Delilah are having a muffled “conversation”    

Kolo pissing into Exmehs caravan, before running off with tongs and a crucible.     

Pilch looks for some general information, specifically against the church. Exposition dump, nothing out of the ordinary other than that constant war with the minons of the (Valkaar) VARG, and those from Lindedorf who are striking back at the church.    

Caravan People Consist of:    
Leader: Hestor    
Guards: Leorable, Dukey, Dallius, Job   
Merchants: Boamos, Tillie, Sabina, Maarah, Sidney      

Troubles in port AbbeyDale in the East, more people from Masooda, Far to the East across the Ocean. Masooda and NanDuan are not friends.    

Story time commences, involving Drop Bears and changelings….    

Changelings are revealed by throwing salt over their right shoulder...


NanDuan has a plethora of sand daggers    

Otario makes friends with a horse, before …    

Kolo goes off for a stealth investigation    

Pilch is caught spooning Hestor    

Fierce discussion takes place about what to do about the ambush. Pilch wants to hide in the, kolo is a fan of stalking the beast    

Pilch has not romanced Hestor after all.    

Hoof prints are massive, but its super light on its feet.    

Probably one of the Nanduisian Balloon Cows    

Otario and Kolo join forces and become Super Mega KolOtariozord, its is not supereffective    

Everyone runs blindly into the woods, some more blindly than others    

Otario prepares the bey blade, but to no avail as she is booted out from underneath kolo, but what is not a flying cow afterall.    

Pilch runs away leaving otario and kolo to die. Luckily the Leucrotta is slain by Riphard awesome boom sticks, and the cross bow bolt of a returning Pilch.    

Exmeh fixes up the axle of the lead wagon and the party moves onto RiverFall which is beautiful.    

In the middle of which is  a large church, the sanctuary of Novetta.    

The spire of “emoticon” -Imota Kan    

Riphard hates women    

Armor is expensive
\clearpage